---
title: "CTutils Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CTutils Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(CTutils)
library(rlang)
library(tibble)
library(dplyr)
library(knitr)

```


# Clinical Trial utilities (CTutils)

CTutils is an R package containing methods to assist in writing
statistical study reports for clinical trials (although the
functions could well be useful in other contexts).

## Example data

To demonstrate these functions, this package contains some 
randomly generated trial data for 50 patients.

```{r example_data}

data(example_trial_data)

glimpse( example_trial.data )

```

There are a number of demographic variables for each patient,
including their trial ID (`Label`), Arm (`Arm`), age (`age`),
Gender (`Gender`) and Ethnicity (`Ethnicity`).

```{r}

example_trial.data %>%
  select( Label, Arm, age, Gender, Ethnicity ) %>%
  head() %>% 
  kable

```

There are then several column containing data representative of
what would be collected via (e)CRF on a clinical trial, including
details about medical history; information about planned/actual
surgical procedures and RECIST assessments at various timepoints.

```{r example_data_accompanying}

patient_data = example_trial.data %>%
  select( -c(Label, Arm, age, Gender, Ethnicity) ) %>%
  head(1) %>% as.list()

tibble( variable = names(patient_data),
        value    = as.character(patient_data) ) %>%
  kable()

```

Also present in this example trial dataset are two
named lists with additional information about each of the
columns in the example trial data: `example_trial.glossary`
provides a readable explanation of each variable in the dataset
and `example_trial.vocabulary` provides a list of the allowed
vocabulary for each categorical variable in the dataset.

```{r glossary_vocabulary}

example_trial.glossary$Week1_Surgery_Planned
example_trial.vocabulary$Week1_Surgery_Planned
```

Note that *all* variables should have an entry in the
`glossary` object, but not all variables need an entry in
the `vocabulary` object (only categorical variables with a
closed vocabulary need to be included here),


```{r}

colnames( example_trial.data ) [ ! colnames( example_trial.data ) %in% names( example_trial.glossary )  ]

v = VennDiagram::venn.diagram(x=list( Data = colnames(example_trial.data),
                                  Glossary = names(example_trial.glossary),
                                  Vocabulary = names(example_trial.vocabulary)),
                          filename=NULL)
grid::grid.draw(v)


```

These `glossary` and `vocabulary` objects will be generated
auotmatically by `10_glossary-extraction.Rmd` and
`11_glossary-munge.Rmd` in the skeleton CTutils pipeline if you are
using it.

## Utility functions

In this section, several utility functions in the CTutils
package will be demonstrated using the example trial data.

### Count up occurences of Yes/No `do_count()`

Count up occurrences of specific results in a column.
By default, the function will count occurrences of
"Yes" and "No".

```{r}

do_count( this_data = example_trial.data,
          this_var  = quo(Screening_PMH_Throm_Y_N),
          key_for_variables = example_trial.glossary
)

```

Providing multiple variables is allowed:

```{r}

do_count( this_data = example_trial.data,
          this_var  = quos(Screening_PMH_Throm_Y_N,
                           Screening_PMH_Cereb_Y_N),
          key_for_variables = example_trial.glossary
)

```

If you ask for a variable that doesn't exist in that
dataset, you will get an error:

```{r}

# ### ERROR
# do_count( this_data = example_trial.data,
#           this_var  = quos(Screening_PMH_Anxiety_Y_N),
#           key_for_variables = example_trial.glossary
# )

```

It may be desirable to show count data for two similar
variables at two different timepoints (e.g., when the same
question is being asked at two different timepoints). Rather than
having to carry out these individual `do_count()` calls and merge
the resulting count tables, the function `do_count_comparison()`
does this for you.

This function first does the two separate `do_count()` function calls,
using the data and variables provided by `this_data`, `group1_variables`
and `group2_variables`. From these count tables, it takes the data as
provided in the specified columns (`group1_column` and `group2_column`)
and merges it together.  Note that for this to work, the glossary terms
for the variables must be identical.

```{r}
do_count_comparison(this_data=example_trial.data,
                    group1_name = "@ Week 1",
                    group1_column = "Yes",
                    group1_variables = quos(Week1_Surgery_NonInvasive_Y_N,
                                            Week1_Surgery_Open_Y_N),
                    group2_name = "@ Surgery",
                    group2_column = "Yes",
                    group2_variables = quos(Surgery_Surgery_NonInvasive_Y_N,
                                            Surgery_Surgery_Open_Y_N),
                    key_for_variables = example_trial.glossary
                    )

```

### Count up occurrences of various levels in a column `do_list_extraction()`

This function is designed to be used where the data in the column
of interest is not just Yes/No, and totals for each value within
that column are desired.

```{r}

do_list_extraction( this_data = example_trial.data,
                    this_var  = quo(Week1_Surgery_Planned),
                    vocab_for_variables = example_trial.vocabulary
)

```

By default, it includes all levels for that variable as defined
by the `vocab_for_variables` parameter, but setting `expand_levels`
to `FALSE` will display counts for ONLY those levels present
in the column.

```{r}
do_list_extraction( this_data = example_trial.data,
                    this_var  = quo(Week1_Surgery_Planned),
                    expand_levels = FALSE,
                    vocab_for_variables = example_trial.vocabulary
)

```

Remove the total by setting `add_total` to `FALSE`.

```{r}

do_list_extraction( this_data = example_trial.data,
                    this_var  = quo(Week1_Surgery_Planned),
                    add_total = FALSE,
                    vocab_for_variables = example_trial.vocabulary
)

```

As with the `do_count()` function, there is a way to combine the 
values of two `do_list_extractions()`: `do_list_comparison()`.

```{r}

do_list_comparison( example_trial.data,
                    group1_variable = quo( Week1_Surgery_Planned ),
                    group1_name = "Planned",
                    group2_variable = quo( Surgery_Surgery_Details ),
                    group2_name = "Actual",
                    vocab_for_variables = example_trial.vocabulary )
 
```

### Summarise numeric data `do_summary()`

The function `do_summary()` will summarise numeric data.
The function will return a list with two objects:

- a table summarising that variable (n, min, median, max etc)
- a boxplot summarising that variable

```{r}

do_summary( example_trial.data,
            this_var = quos(age, age),
            key_for_variables = example_trial.glossary )

```

It is possible to provide `do_summary()` with more than
one variable if the summary statistics/boxplots should be shown
side by side.

