```{r title_page}
include_graphics( path = REPORT.BANNER.IMG )
```

**`r TRIAL.NAME`**

`r TRIAL.DESCRIPTION`

**`r REPORT.TYPE` report**

|                    |                                         |
| ------------------ | --------------------------------------- |
| *Report version*     | `r REPORT.VERSION`                      |
| *Report Date*        | `r format(today(),format="%d %B %Y")`   |
| *Database lock date* | `r format(as.Date(EXTRACT.DATE,format="%Y-%m-%d"),format="%d %B %Y")` |
| *Author*             | `r REPORT.AUTHOR.NAME`                       |

**Trial documentation**

|                    |                                         |
| ------------------ | --------------------------------------- |
| *Protocol*         | v. `r PROTOCOL.VERSION` |
| *SAP*              | v. `r SAP.VERSION`      |
| *Trial Coordinating Centre* | Cancer Clinical Trials Unit, Scotland (CaCTUS). |
|                             | Scottish Clinical Trials Research Unit (SCTRU), Edinburgh. |

**External identifiers**

|                |                |
| -------------- | -------------- |
| ISRCTN         | `r TRIAL.ID.ISRCTN`  |
| EudraCT Number | `r TRIAL.ID.EudraCT` |
| REC reference  | `r TRIAL.ID.REC`     |


**Checked, reviewed and approved by**

```{r checkandreview_chunk}

reviewing.info = tribble(
  ~Role                    ,~Name           ,~Signature,~Date,
  "Statistician (author)"  , REPORT.AUTHOR.NAME  ,        NA,   NA,
  "Statistician (reviewer)", REPORT.REVIEWER.NAME,        NA,   NA#,
  #"Chief investigator"     ,              NA,        NA,   NA
)

if ( PIPELINE.FLEXTABLE ) {
flextable(reviewing.info) %>%
  autofit() %>%
  bold( bold = TRUE, part = "header" ) %>%
  border_remove() %>%
  bg( part="header", bg=tbl_fill.colours[["grey"]]) %>%
  border(j=3, part="body",border = tbl_border.standard) %>%
  width(j=3, width=1.5) %>%
  width(j=4, width=0.7) %>%
  height(height=0.7) %>%
  align(part="header",align="left") %>%
  valign(part="body",valign="top") 
} else {
  knitr::kable( reviewing.info )
}

```

`r ifelse( REPORT.TYPE=="Final", "", "NB. CI approval only required for final report" )`

**Author contact details**

|               |                 |
| ------------- | --------------- |
| Name          | `r REPORT.AUTHOR.NAME`   |
| Affiliation   | `r REPORT.AUTHOR.ORGANISATION`   |
| Email address | `r REPORT.AUTHOR.EMAIL` |
| Phone         | `r REPORT.AUTHOR.PHONE` |

