<!-- Add additional analyses as defined by the SAP -->

# Baseline data and demographic characteristics

**Static text should be formatted in bold**

Interpretative text should be formatted as normal so that it can
be easily checked between DMCs.

## Patient and disease characteristics

### Registering centre

```{r registering_centre}

```

### Age at randomisation

```{r age_at_randomisation}

```

### Gender at randomisation

```{r gender_at_randomisation}

```

### Baseline stratification factors

```{r baseline_stratification_factors}

```

### Baseline disease characteristics

```{r baseline_disease_characteristics}

```

## Pre-treatment investigations

### Investigations to ensure eligibility criteria met

```{r eligibility_criteria_investigations}

```

### Investigations to identify tumour

```{r investigations_to_identify_tumour}

```

## Significant Medical History/Existing Symptoms & Signs 

### Cardiac history 

```{r cardiac_history}

```

### Other cardiac history

```{r cardiac_history_other}
 
```

### Respiratory Disease 

```{r respiratory_disease}

```

### Other respiratory disease 

```{r respiratory_disease_other}

```

### Other medical history

```{r other_medical_history}

```

### Conditions/Symptoms/signs caused by concomitant illnesses and medications 

```{r concomitant_conditions}

```

## Concomitant Medication details

### Details of concomitant medication 

```{r concomitant_medicine_details}

```

### Number of patients taking medication for XX 

```{r XX_medication}

```

### Changes to concomitant medications 

```{r concomitant_changes}

```


