# EUdraCT report

**The information required for the EudraCT upload is provided in this report.
Also generated is an XML file for the adverse events upload.**

**This report is heavily reliant on the relevant information being completed
in the settings.yml file. Please ensure that this file is fully population
withthe relevant information.**

```{r Eudract_intro}

vocab = CTutils::read_EudraCT_vocabulary()

EUdraCT_vocabulary = vocab$EudraCT
RMS_vocabulary = vocab$RMS

print_info = function( info_var ) {
  info_var.string = deparse(substitute(info_var))
  if( !exists(info_var.string) ) {
    info_var = "[MISSING]"
  }
  return( info_var )
}

```



## Trial index

|                        |                                         |
| ---------------------- | --------------------------------------- |
| *Friendly description* | `r print_info(TRIAL.DESCRIPTION)`       |

Summary attachments to include:

1. Final report to DMC
2. Published article

## Trial information

### Trial identification

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **EudraCT number** | `r print_info(TRIAL.ID.EudraCT)` |
| **Sponsor protocol code** | `r print_info(TRIAL.NAME)` v. `r print_info(PROTOCOL.VERSION)` (dated `r print_info(PROTOCOL.DATE)`) |
| **Full title of trial** | `r print_info(TRIAL.DESCRIPTION)` |


### Additional Study identifiers

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **ISRCTN number** | `r print_info(TRIAL.ID.ISRCTN)` |
| **ClinicalTrials.gov number** | `r print_info( TRIAL.ID.NCT )` |
| **WHO universal trial number** | `r print_info( TRIAL.ID.WHO )` |

Other identifiers provided:


```{r results="asis"}

other_ids = ls( pattern="TRIAL\\.ID\\..*" ) %>% 
  discard( ~ str_detect(.x, pattern="ISRCTN|REC|EudraCT") )

if ( length( other_ids ) > 0 ) {
  
  other_ids.list = map( other_ids, get ) %>%
    set_names( other_ids %>% str_replace( "TRIAL\\.ID\\.", "" ) )
  
  for( id_i in 1:length(other_ids.list) ) {
    
    cat( sprintf( "- **%s ID**: %s\n",
                  names(other_ids.list)[id_i],
                  other_ids.list[id_i]) )
  }
} else {
  cat( sprintf( "No other trial identifiers have been specified." ))
}

```

## Sponsor details

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Name of organisation** | `r print_info( SPONSOR.NAME )` |
| **Street address** | `r print_info( SPONSOR.ADDRESS.STREET )` |
| **Town/city** | `r print_info( SPONSOR.ADDRESS.CITY )` |
| **Postcode** | `r print_info( SPONSOR.ADDRESS.POSTCODE )` |

### Scientific contact point

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Name of organisation** | `r print_info( SPONSOR.SCIENTIFIC_CONTACT.ORGANISATION )` |
| **Functional contact point name** | `r print_info( SPONSOR.SCIENTIFIC_CONTACT.NAME )` |
| **Telephone number** | +`r print_info( SPONSOR.SCIENTIFIC_CONTACT.TELEPHONE.COUNTRY_CODE)` `r print_info( SPONSOR.SCIENTIFIC_CONTACT.TELEPHONE.NUMBER)` |
| **Email address** | `r print_info( SPONSOR.SCIENTIFIC_CONTACT.EMAIL)` |

### Public contact point

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Name of organisation** | `r print_info( SPONSOR.PUBLIC_CONTACT.ORGANISATION )` |
| **Functional contact point name** | `r print_info( SPONSOR.PUBLIC_CONTACT.NAME )` |
| **Telephone number** | +`r print_info( SPONSOR.PUBLIC_CONTACT.TELEPHONE.COUNTRY_CODE)` `r print_info( SPONSOR.PUBLIC_CONTACT.TELEPHONE.NUMBER)` |
| **Email address** | `r print_info( SPONSOR.PUBLIC_CONTACT.EMAIL)` |


## Paediatric regulatory details

**Is trial part of an agreed paediatric investigation plan (PIP)?** `r print_info(EUDRACT.PAEDIATRIC.PIP)`

**Does article 45 of Regulation (EC) No 1901/2006 apply to this trial?** `r print_info(EUDRACT.PAEDIATRIC.ARTICLE_45_APPLIES)`

**Does article 46 of Regulation (EC) No 1901/2006 apply to this trial?** `r print_info(EUDRACT.PAEDIATRIC.ARTICLE_46_APPLIES)`


## Results analysis stage

```{r}

# date_of_final_analysis = format(as.Date(EXTRACT.DATE,format="%Y-%m-%d"),format="%d %B %Y")
# 
# primary_completion_date = ITT_population.d_extended %>%
#   select( Label, ends_with( "Date_Form_Comp" ) ) %>%
#   select( -contains( "Scan_review" ) ) %>% 
#   pivot_longer( -Label ) %>% arrange( desc(dmy(value)) ) %>%
#   pull( value ) %>%
#   head(1) %>%
#   as.character()
# 
# last_appointment_columns = grep( ls( ), pattern = "EUDRACT.LAST_APPOINTMENT", value=T ) %>% 
#   lapply( get ) %>% unlist 
# 
# global_end_of_trial_date = ITT_population.d_extended %>%
#   select( Label, !!!syms( last_appointment_columns ) ) %>% 
#   pivot_longer( -Label ) %>% 
#   filter( value != "" ) %>% 
#   arrange( desc( dmy(value) ) ) %>% 
#   pull( value ) %>% 
#   head(1) %>% 
#   as.character() 


```


|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Analysis stage** | `r print_info( REPORT.TYPE )` |
| **Date of interim/final analysis** | `r date_of_final_analysis` |


|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Is this the analysis of the primary completion data?** | TBD |
| **Primary completion date** | `r primary_completion_date` |

|                        |                                         |
| ---------------------- | --------------------------------------- |
| **Global end of trial date reached?** | Yes |
| **Global end of trial date** | `r global_end_of_trial_date` |
| **Was the trial ended prematurely?** | No |


## General information about the trial

**Main objective of the trial**

`r TRIAL.PRIMARY_OBJECTIVE`

**Actual start date of recruitment**

`r TRIAL.START_DATE %>% as.character`

**Long term follow-up planned?**

`r EUDRACT.LTFU_PLANNED`

**Independent data monitoring committee (IDMC) involvement?**

`r ( DMC.COMMITTEE %>% nrow ) > 1 `

**Protection of trial subjects**

`r print_info( EUDRACT.SUBJECT_PROTECTION )`

**Background therapy**

`r print_info( EUDRACT.NON_TEST_OR_COMPARATOR_TREATMENTS )`

**Evidence for comparator(s)**

`r print_info( EUDRACT.COMPARATOR_RATIONALE )`

## Population of trial subjects

### Subject number per country

**Note that this information may need to be added to the relevant
data frame.**

```{r country_counts}

if ( str_detect( "Country", EudraCT_data %>% colnames ) %>% any ) {
  
  countries = EudraCT_data %>%
    select( Label, Country ) %>%
    unique %>% pull( Country )
  
  country_table = table( countries ) %>%
    as_tibble( )
  
  country_table = country_table %>% 
    add_row( countries = "Total",
             n = sum( country_table$n ))
  
  knitr::kable( country_table )
}

```

**Age group breakdown for trial**

```{r agegroups}
agegroup.tibble = EudraCT_data$EudraCT_agegroup %>%
  discard( ~is.na(.x) ) %>%
  as_tibble %>%
  group_by( value, .drop=FALSE ) %>%
  dplyr::summarise( count = n() ) %>%
  mutate( value = as.character(value)) %>% 
  dplyr::rename( Agegroup = value )

knitr::kable( agegroup.tibble )

```

## Subject disposition

**Recruitment details**

`r print_info(EUDRACT.RECRUITMENT_DETAILS)`

## Pre-assignment

**Screening details**

`r print_info(EUDRACT.SCREENING_DETAILS)`

## Arm information (copy this section for each arm)

```{r}
# patients_enrolled = ITT_population.d_extended %>%
#   filter( Label != "" ) %>%
#   pull(Label) %>%
#   unique ()
# 
# patients_dropouts = ITT_population.d_extended %>%
#   filter( Miscellaneous_Early_Termin_Trial_ID != "" ) %>%
#   select( Label, starts_with( "Miscellaneous_Early_Termin" ) ) %>%
#   pull( Label ) %>%
#   unique()
# 
# n_enrolled = patients_enrolled %>% length( ) 
# n_completed = setdiff( patients_enrolled, patients_dropouts ) %>% length( )

```


<!--Number of patients who started on this arm: `r n_enrolled`
Number of patients who finished on this arm: `r n_completed`-->



Reasons for dropping out:

Disease progression:

```{r}

# do_count( this_data = ITT_population.d_extended %>%
#             filter( Miscellaneous_Early_Termin_Trial_ID != "" ),
#           this_var = quo( Miscellaneous_Early_Termin_ET_Dis_Prog ),
# 	  key_for_variables = glossary.key,
# 	  missing_data_limit = PIPELINE.MISSING_DATA_LIMIT )

```

Other reasons:

```{r}
# 
# do_count( this_data = ITT_population.d_extended %>%
#             filter( Miscellaneous_Early_Termin_Trial_ID != "" ) %>% 
#             filter( Miscellaneous_Early_Termin_ET_Other_Reas  == "Yes"),
#           this_var = quos( Miscellaneous_Early_Termin_ET_Wthdrw_Cons,
#                            Miscellaneous_Early_Termin_ET_Pat_LTFU,
#                            Miscellaneous_Early_Termin_ET_PI_Decision,
#                            Miscellaneous_Early_Termin_ET_Non_Comply,
#                            Miscellaneous_Early_Termin_ET_Not_Start,
#                            Miscellaneous_Early_Termin_ET_Death ),
# 	  key_for_variables = glossary.key,
# 	  missing_data_limit = PIPELINE.MISSING_DATA_LIMIT )
# 
# reason_per_patient = ITT_population.d_extended %>%
#   filter( Miscellaneous_Early_Termin_Trial_ID != "" ) %>% 
#   filter( Miscellaneous_Early_Termin_ET_Other_Reas  == "Yes") %>%
#   select( Label,
#           Miscellaneous_Early_Termin_ET_Wthdrw_Cons,
#           Miscellaneous_Early_Termin_ET_Pat_LTFU,
#           Miscellaneous_Early_Termin_ET_PI_Decision,
#           Miscellaneous_Early_Termin_ET_Non_Comply,
#           Miscellaneous_Early_Termin_ET_Not_Start,
#           Miscellaneous_Early_Termin_ET_Death )
# 
# reason_check = reason_per_patient %>% 
#   pivot_longer( -Label,
#                 names_to = "reason",
#                 values_to = "response") %>% 
#   group_by( Label ) %>% 
#   summarise( REASON_PRESENT = any( response == "Yes"))

```

`r ifelse( reason_check %>% pull( REASON_PRESENT ) %>% all, "", print_error( "Not all patients have a reason provided." ) )`

```{r}

# knitr::kable(PERIOD.INFO %>%
#                mutate(section_header = sprintf("**%s**",section_header)) %>%
#                mutate(section_header = str_replace(section_header,"\\*\\*\\*\\*","")) %>%
#                mutate(question = sprintf("**%s**",question)) %>% 
#                mutate(question = str_replace(question,"\\*\\*\\*\\*","")),
#              col.names=rep.int("",ncol(PERIOD.INFO)))
 
```

## Number of patients in each population (e.g., ITT, safety etc)

<!--ITT: `r n.ITT`-->
<!--Evaluable: `r n.evaluable`-->
<!--Safety: `r n.evaluable`-->

## Age/gender counts per population

### ITT population

```{r}

# ITT_population.d %>% pull( EudraCT_agegroup ) %>% table
# 
# do_summary(ITT_population.d,
#            quo( Age),
# 	  key_for_variables = glossary.key,
# 	  missing_data_limit = PIPELINE.MISSING_DATA_LIMIT )
# 
# ITT_population.d %>% pull( Enrolment_Trial_Enrolment_Sex ) %>% table


```

### Safety/evaluable population

```{r}

# treated_population.d %>% pull( EudraCT_agegroup ) %>% table
# 
# do_summary(treated_population.d,
#            quo( Age),
# 	  key_for_variables = glossary.key,
# 	  missing_data_limit = PIPELINE.MISSING_DATA_LIMIT )
# 
# treated_population.d %>% pull( Enrolment_Trial_Enrolment_Sex ) %>% table

```

### Surgical population

```{r}
# 
# ITT_population.d %>% filter( SURGERY_PERFORMED == "Yes" ) %>%  pull( EudraCT_agegroup ) %>% table
# 
# do_summary(ITT_population.d %>% filter( SURGERY_PERFORMED == "Yes" ),
#            quo( Age),
# 	  key_for_variables = glossary.key,
# 	  missing_data_limit = PIPELINE.MISSING_DATA_LIMIT )
# 
# ITT_population.d %>% pull( Enrolment_Trial_Enrolment_Sex ) %>% table


```

## Generating the SAE and AE XML uploads for EudraCT

```{r CTCAE1}

### Example shown below 

# SAE.data = ITT_population.d_extended %>%
#   filter( !is.na(SAE_Reporting_SAE_SAE_Num) ) %>%
#   select( SAE_Reporting_SAE_SAE_Num,
#           Label,
#           
#           # SAE_Reporting_SAE_SAE_Axi_Related,
#           SAE_Reporting_SAE_SAE_Oth_Related,
#           SAE_Reporting_SAE_SAE_Oth_Spec,
#           SAE_Reporting_SAE_SAE_Pro_Related,
#           SAE_Reporting_SAE_SAE_Pro_Spec,
#           
#           SAE_Reporting_SAE_2_SAE_Ax_TDD,
#           SAE_Reporting_SAE_2_SAE_Ax_Freq,
#           SAE_Reporting_SAE_2_SAE_Ax_Start,
#           SAE_Reporting_SAE_2_SAE_Ax_Stop,
#           SAE_Reporting_SAE_SAE_Event,
#           SAE_Reporting_SAE_SAE_Symp_Start,
#           
#           # SAE type?
#           SAE_Reporting_SAE_SAE_Death,
#           SAE_Reporting_SAE_SAE_Hosp,
#           SAE_Reporting_SAE_SAE_Defect,
#           SAE_Reporting_SAE_SAE_Life,
#           SAE_Reporting_SAE_SAE_Incapacity,
#           SAE_Reporting_SAE_SAE_Important,
#           
#           SAE_Reporting_SAE_SAE_Grade,
#           SAE_Reporting_SAE_SAE_Axi_Related, # site investigator causailty
#           SAE_Reporting_SAE_SAE_CI_Cause,    # CI causality
#           SAE_Reporting_SAE_SAE_Exp_Unexp,
#           
#           ### SUSAR?          
#           #SAE_Reporting_SAE_SAE_Exp_Unexp = Unexpected
#           #SAE_Reporting_SAE_SAE_CI_Cause = YES
#           
#           SAE_Reporting_SAE_2_SAE_Outcome
#   ) %>%
#   group_by( SAE_Reporting_SAE_SAE_Num ) %>%
#   mutate( SUSAR = ifelse(SAE_Reporting_SAE_SAE_Exp_Unexp=="Unexpected" &
#                            SAE_Reporting_SAE_SAE_CI_Cause=="Yes",
#                          "Yes","No"),
#           SAEtype = paste(
#             ifelse(SAE_Reporting_SAE_SAE_Death=="Yes",
#                    "Death",
#                    ""),
#             ifelse(SAE_Reporting_SAE_SAE_Hosp =="Yes",
#                    "Hospitalisation",
#                    ""),
#             ifelse(SAE_Reporting_SAE_SAE_Defect=="Yes",
#                    "Birth defect",
#                    ""),
#             ifelse(SAE_Reporting_SAE_SAE_Life=="Yes",
#                    "Life threatening",
#                    ""),
#             ifelse(SAE_Reporting_SAE_SAE_Incapacity=="Yes",
#                    "Disability/incapacity",
#                    ""),
#             collapse="\n"
#           ) ) %>%
#   select( -SAE_Reporting_SAE_SAE_Death,
#           -SAE_Reporting_SAE_SAE_Hosp,
#           -SAE_Reporting_SAE_SAE_Defect,
#           -SAE_Reporting_SAE_SAE_Life,
#           -SAE_Reporting_SAE_SAE_Incapacity,
#           -SAE_Reporting_SAE_SAE_Important) %>%
#   
#   mutate( suspect = paste(
#     ifelse(SAE_Reporting_SAE_SAE_Pro_Related=="Yes",
#            sprintf( "%s: %s",
#                     glossary.key[["SAE_Reporting_SAE_SAE_Pro_Related"]],
#                     SAE_Reporting_SAE_SAE_Pro_Spec),
#            ""),
#     ifelse(SAE_Reporting_SAE_SAE_Oth_Related=="Yes",
#            sprintf( "%s: %s",
#                     glossary.key[["SAE_Reporting_SAE_SAE_Oth_Related"]],
#                     SAE_Reporting_SAE_SAE_Oth_Spec),
#            ""),
#     collapse="\n"
#   ) ) %>%
#   select( -SAE_Reporting_SAE_SAE_Oth_Related,
#           -SAE_Reporting_SAE_SAE_Oth_Spec,
#           -SAE_Reporting_SAE_SAE_Pro_Related,
#           -SAE_Reporting_SAE_SAE_Pro_Spec ) %>%
#   mutate(IMPdose = sprintf( "%s, %s",
#                             SAE_Reporting_SAE_2_SAE_Ax_TDD,
#                             SAE_Reporting_SAE_2_SAE_Ax_Freq)) %>%
#   select( -SAE_Reporting_SAE_2_SAE_Ax_TDD,
#           -SAE_Reporting_SAE_2_SAE_Ax_Freq ) %>%
#   mutate( studydrug = sprintf( "Started: %s\nStopped: %s",
#                                dmy(SAE_Reporting_SAE_2_SAE_Ax_Start),
#                                dmy(SAE_Reporting_SAE_2_SAE_Ax_Stop) )) %>%
#   select( -SAE_Reporting_SAE_2_SAE_Ax_Start,
#           -SAE_Reporting_SAE_2_SAE_Ax_Stop ) %>%
#   select( SAE_Reporting_SAE_SAE_Num,
#           Label,
#           suspect,
#           IMPdose,
#           studydrug,
#           SAE_Reporting_SAE_SAE_Event,
#           SAE_Reporting_SAE_SAE_Symp_Start,
#           SAEtype,
#           SAE_Reporting_SAE_SAE_Grade,
#           SAE_Reporting_SAE_SAE_Axi_Related,
#           SAE_Reporting_SAE_SAE_CI_Cause,
#           SAE_Reporting_SAE_SAE_Exp_Unexp,
#           SUSAR,
#           SAE_Reporting_SAE_2_SAE_Outcome
#   ) %>%
#   arrange( SAE_Reporting_SAE_SAE_Num ) %>% 
#   mutate( description = SAE_Reporting_SAE_SAE_Event )
# 
# 
# 
# print_flextable( SAE.data,
#                  column_recode = list(
#                    Label = "Patient",
#                    SAE_Reporting_SAE_SAE_Num = "SCTRU SAE No.",
#                    description = "SAE event term",
#                    SAE_Reporting_SAE_SAE_Grade = "CTC Grade V4.0",
#                    SAE_Reporting_SAE_SAE_Symp_Start = "Onset Date",
#                    SAE_Reporting_SAE_SAE_Axi_Related = "Causality Assessment of Site I",
#                    SAE_Reporting_SAE_SAE_CI_Cause = "Causality Assessment of CI",
#                    SAE_Reporting_SAE_SAE_Exp_Unexp = "Expectedness Assessment of CI",
#                    SAE_Reporting_SAE_2_SAE_Outcome = "SAE Outcome",
#                    SUSAR = "SUSAR?",
#                    SAEtype = "SAE Type",
#                    suspect = "Suspect drug/procedure",
#                    IMPdose = "IMP Dose & route",
#                    studydrug = "Date study drug started and stopped"
#                  ))
# 
# 
# AE.data = toxicity_ALL.d %>% filter( value > 0 ) %>%
#   dplyr::rename( description = toxicity_description )

```

```{r}

# if ( EUDRACT.MEDDRA_SAE.FILE != "" & file.exists( paste( EUDRACT.MEDDRA_SAE.LOCATION,
#                          EUDRACT.MEDDRA_SAE.FILE,
#                          sep="/") ) ) {
#   
#   SAE_MedDRA_encoding.in = read_xlsx( paste( EUDRACT.MEDDRA_SAE.LOCATION,
#                          EUDRACT.MEDDRA_SAE.FILE,
#                          sep="/") ) %>% 
#     mutate( soc_term = ifelse( is.na(`SOC confirmed`),
#                            `SOC proposed`,
#                            `SOC confirmed` ) )
#   
#   SAE_MedDRA_encoding = SAE_MedDRA_encoding.in  %>% 
#     inner_join( eudract::soc_code %>% 
#                   select( soc_term,
#                           meddra ),
#                 by="soc_term" ) %>% 
#     dplyr::rename( soc = meddra )
#   
#   
#   SAE_MedDRA_merge = SAE.data %>% 
#     inner_join( SAE_MedDRA_encoding, by=c( "Label", "description" ) ) %>% 
#     mutate( pt = NA ) %>% 
#     dplyr::rename( subjid = Label ) %>% 
#     dplyr::rename( related = SAE_Reporting_SAE_SAE_CI_Cause ) %>% 
#     mutate( fatal = case_when(
#       SAE_Reporting_SAE_2_SAE_Outcome == "Death" ~ 1,
#       TRUE ~ 0 ) ) %>% 
#     mutate( serious = 1 ) %>% 
#     mutate( group = "Single" ) %>% 
#     mutate( term = soc_term ) %>% 
#     select( pt, # CAN BE NA
#             subjid, # Label
#             related, # SAE.data$SAE_Reporting_SAE_SAE_CI_Cause
#             soc, # got this in SAE_MedDRA_encoding$soc
#             fatal, # SAE.data$SAE_Reporting_SAE_2_SAE_Outcome
#             serious, # this will be 1 for SAEs
#             group, # which arm - what to do if there is only one?
#             term # SAE_MedDRA_encoding$soc_term
#     )
# }
# 
# 
# SAE_MedDRA_merge = tibble()
# AE_MedDRA_merge = tibble()
# 
# 
# if ( EUDRACT.MEDDRA_SAE.FILE != "" & file.exists( paste( EUDRACT.MEDDRA_SAE.LOCATION,
#                          EUDRACT.MEDDRA_SAE.FILE,
#                          sep="/") ) ) {
#   
#   SAE_MedDRA_encoding.in = read_xlsx( paste( EUDRACT.MEDDRA_SAE.LOCATION,
#                          EUDRACT.MEDDRA_SAE.FILE,
#                          sep="/") ) %>% 
#     mutate( soc_term = ifelse( is.na(`SOC confirmed`),
#                            `SOC proposed`,
#                            `SOC confirmed` ) )
#   
#   SAE_MedDRA_encoding = SAE_MedDRA_encoding.in  %>% 
#     inner_join( eudract::soc_code %>% 
#                   select( soc_term,
#                           meddra ),
#                 by="soc_term" ) %>% 
#     dplyr::rename( soc = meddra )
#   
#   
#   SAE_MedDRA_merge = SAE.data %>% 
#     full_join( SAE_MedDRA_encoding, by=c( "Label", "description" ) ) %>% 
#     mutate( pt = NA ) %>% 
#     dplyr::rename( subjid = Label ) %>% 
#     dplyr::rename( related = SAE_Reporting_SAE_SAE_CI_Cause ) %>% 
#     mutate( fatal = case_when(
#       SAE_Reporting_SAE_2_SAE_Outcome == "Death" ~ 1,
#       TRUE ~ 0 ) ) %>% 
#     mutate( serious = 1 ) %>% 
#     mutate( group = "Single" ) %>% 
#     mutate( term = soc_term ) %>% 
#     select( pt, # CAN BE NA
#             subjid, # Label
#             related, # SAE.data$SAE_Reporting_SAE_SAE_CI_Cause
#             soc, # got this in SAE_MedDRA_encoding$soc
#             fatal, # SAE.data$SAE_Reporting_SAE_2_SAE_Outcome
#             serious, # this will be 1 for SAEs
#             group, # which arm - what to do if there is only one?
#             term # SAE_MedDRA_encoding$soc_term
#     )
# } else {
#  print_warning( "MedDRA coding not provided for SAEs" )
#   
# }
# 
# 
# if ( EUDRACT.MEDDRA_SAE.FILE != "" & file.exists( paste( EUDRACT.MEDDRA_AE.LOCATION,
#                          EUDRACT.MEDDRA_AE.FILE,
#                          sep="/") ) ) {
#   
#   AE_MedDRA_encoding.in = read_xlsx( paste( EUDRACT.MEDDRA_AE.LOCATION,
#                          EUDRACT.MEDDRA_AE.FILE,
#                          sep="/") ) %>% 
#     mutate( soc_term = ifelse( is.na(`SOC confirmed`),
#                            `SOC proposed`,
#                            `SOC confirmed` ) )
#   
#   AE_MedDRA_encoding = AE_MedDRA_encoding.in  %>% 
#     left_join( eudract::soc_code %>% 
#                   select( soc_term,
#                           meddra ),
#                 by="soc_term" ) %>% 
#     dplyr::rename( soc = meddra ) %>% 
#     select( -Label )
#   
#   AE_MedDRA_merge = AE.data %>% 
#     full_join( AE_MedDRA_encoding, by="description" ) %>% 
#     mutate( pt = NA ) %>% 
#     dplyr::rename( subjid = Label ) %>%
#     ### Where is the relatedness information for the AEs?
#     dplyr::mutate( related = "Yes" ) %>% 
#     mutate( fatal = 0 ) %>% 
#     mutate( serious = 0 ) %>% 
#     mutate( group = "Single" ) %>% 
#     mutate( term = soc_term ) %>% 
#     select( pt, # CAN BE NA
#             subjid, # Label
#             related, # SAE.data$SAE_Reporting_SAE_SAE_CI_Cause
#             soc, # got this in SAE_MedDRA_encoding$soc
#             fatal, # SAE.data$SAE_Reporting_SAE_2_SAE_Outcome
#             serious, # this will be 1 for SAEs
#             group, # which arm - what to do if there is only one?
#             term # SAE_MedDRA_encoding$soc_term
#     )
# } else {
#  print_warning( "MedDRA coding not provided for SAEs" )
#   
# }
# 
# ALL_ADVERSE_EVENTS = SAE_MedDRA_merge %>% 
#   bind_rows( AE_MedDRA_merge ) %>% 
#   dplyr::mutate( related = case_when(
#     related == "No" ~ FALSE,
#     related == "Yes" ~ TRUE,
#     TRUE ~ NA
#   ))
# 
# 
# 
# ### Enter the number of subjects in this reporting group 
# ### exposed to the treatment. It is assumed that all subjects
# ### who received at least one dose of the treatment are
# ### included in the reporting group.
# subjectsExposed = c(Single=n.ITT)
# 
# ### Enter the number of deaths in this reporting group.
# ### This includes deaths not related to the trial.
# # count of deaths not in the Safety data. Could be c(0,0)
# deathsExternal  = c(Single=ITT_population.d %>%
#                       filter( Miscellaneous_Death_Trial_ID != "" ) %>% 
#                       pull( Miscellaneous_Death_Trial_ID ) %>% 
#                       unique %>% length)
# 
# 
# safety_statistics = safety_summary(ALL_ADVERSE_EVENTS,
#                                    exposed=subjectsExposed,
#                                    excess_deaths=deathsExternal,
#                                    freq_threshold = 0
# )
# 
# simple <- tempfile(fileext = ".xml")
# eudract_upload_file <- sprintf( "%s/safety_upload.xml", EUDRACT.XML.LOCATION )
# 
# simple_safety_xml(safety_statistics, simple)
# eudract_convert(input=simple,
#                 output=eudract_upload_file)
#   
# myschema <- xml2::read_xml(system.file("extdata","adverseEvents.xsd", package="eudract"))
# aes <- xml2::read_xml(eudract_upload_file)
# check <- xml2::xml_validate(aes,myschema)
# if(check){print("Validation against the schema has passed!")}


```


## Generating data in ClinicalTrials.gov format

Tables to be in the following format. These can be generated from the
same Excel spreadsheets as were used to populate the EudraCT XML.


| Preferred Term    | SOC term                    | N patients | N events |
| :---------------- | :-------------------------- | ---------: | -------: | 
| Cardiac arrest    | Cardiac disorders           |          1 |        3 |
| Confusional state | Psychiatric disorders       |          1 |        1 |
| Hematuria         | Renal and urinary disorders |          2 |        2 |
| Hyperglycemia     | Endocrine disorders         |          1 |        1 |

There are to be two separate tables - one for SAEs and one for AEs.

Also needing to be generated is the number of patients who were affected
by at least one SAE and at least one AE.


```{r}
# 
# SAE_MedDRA_encoding.in = read_xlsx( paste( EUDRACT.MEDDRA_SAE.LOCATION,
#                        EUDRACT.MEDDRA_SAE.FILE,
#                        sep="/") ) %>% 
#   mutate( soc_term = ifelse( is.na(`SOC confirmed`),
#                          `SOC proposed`,
#                          `SOC confirmed` ) ) %>% 
#   mutate( pt_term = ifelse( is.na(`Term confirmed`),
#                          `Term proposed`,
#                          `Term confirmed` ) )
# 
# SAE_MedDRA_encoding = SAE_MedDRA_encoding.in  %>%
#   inner_join( eudract::soc_code %>%
#                 select( soc_term,
#                         meddra ),
#               by="soc_term" ) %>%
#   dplyr::rename( soc = meddra )
# 
# 
# SAE_MedDRA_encoding %>%
#   group_by( pt_term, soc_term ) %>%
#   summarise( n_patients = length( unique( Label ) ),
#              n_events = n() ) %>% 
#   print_flextable
#   
# SAE_MedDRA_encoding %>% pull( Label ) %>% unique %>% length
  
```

```{r}

# AE_MedDRA_encoding.in = read_xlsx( paste( EUDRACT.MEDDRA_AE.LOCATION,
#                          EUDRACT.MEDDRA_AE.FILE,
#                          sep="/") ) %>% 
#   mutate( soc_term = ifelse( is.na(`SOC confirmed`),
#                          `SOC proposed`,
#                          `SOC confirmed` ) ) %>% 
#   mutate( pt_term = ifelse( is.na(`Term confirmed`),
#                          `Term proposed`,
#                          `Term confirmed` ) )
#   
# AE_MedDRA_encoding = AE_MedDRA_encoding.in  %>% 
#     left_join( eudract::soc_code %>% 
#                   select( soc_term,
#                           meddra ),
#                 by="soc_term" ) %>% 
#     dplyr::rename( soc = meddra ) %>% 
#     select( -Label )
#   
# AE_MedDRA_merge = AE.data %>% 
#     full_join( AE_MedDRA_encoding, by="description" ) %>% 
#     select( pt_term, # CAN BE NA
#             Label, # Label
#             soc_term # SAE_MedDRA_encoding$soc_term
#     )
# 
# AE_MedDRA_merge %>%
#   group_by( pt_term, soc_term ) %>%
#   summarise( n_patients = length( unique( Label ) ),
#              n_events = n() ) %>% 
#   print_flextable


# AE_MedDRA_merge %>% pull( Label ) %>% unique %>% length

```